---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(datacenter)
```
# datacenter

The goal of datacenter is to assist in the consolidation of information spread 
across multiple data sets.

## Installation

<!-- You can install the released version of datacenter from [CRAN](https://CRAN.R-project.org) with: -->

``` r
install.packages("datacenter")
```

You can install the development version of datacenter from [Github](https://github.com/mkearney/datacenter) with:

``` r
remotes::install_github("mkearney/datacenter")
```


## Example

Let's say you want to consolidate and maximize information (variables) for 
obversations spread across multiple different data sets.

```{r example}
## data set with variables v1, v2
data1 <- tibble::tibble(
  id = c("a", "b", "c"),
  v1 = c(TRUE, FALSE, FALSE),
  v2 = c(1, NA_real_, NA_real_)
)

## data set with variables v2, v3
data2 <- tibble::tibble(
  id = c("b", "c"),
  v2 = c(2, 3),
  v3 = c("z", "x")
)
```

Create a data center with a fixed set of variables

```{r}
## create data center with all variables
dc <- new_datacenter(c(names(data1), names(data2)))

## print datacenter
dc
```


```{r}
## add data1 to datacenter
dc$add(data1)
dc

## update datacenter with data2
dc$update(data2)
dc
```

